% resume.tex
% vim:set ft=tex spell:

\documentclass[11pt,letterpaper]{article}
\usepackage[letterpaper,margin=0.75in]{geometry}
\usepackage[utf8]{inputenc}
\usepackage{mdwlist}
\usepackage[T1]{fontenc}
\usepackage{textcomp}
\usepackage{tgpagella}
\usepackage{hyperref}
\pagestyle{empty}
\setlength{\tabcolsep}{0em}

% indentsection style, used for sections that aren't already in lists
% that need indentation to the level of all text in the document
\newenvironment{indentsection}[1]%
{\begin{list}{}%
	{\setlength{\leftmargin}{#1}}%
	\item[]%
}
{\end{list}}

% opposite of above; bump a section back toward the left margin
\newenvironment{unindentsection}[1]%
{\begin{list}{}%
	{\setlength{\leftmargin}{-0.5#1}}%
	\item[]%
}
{\end{list}}

% format two pieces of text, one left aligned and one right aligned
\newcommand{\headerrow}[2]
{\begin{tabular*}{\linewidth}{l@{\extracolsep{\fill}}r}
	#1 &
	#2 \\
\end{tabular*}}

% make "C++" look pretty when used in text by touching up the plus signs
\newcommand{\CPP}
{C\nolinebreak[4]\hspace{-.05em}\raisebox{.22ex}{\footnotesize\bf ++}}

% and the actual content starts here
\begin{document}

\begin{center}
{\LARGE \textbf{Jeremy G. Giese}}
\bigbreak
%269 Rowan Rd.~\smallbreak
%\ \ White Sulphur Springs, WV 24986\smallbreak\
(304) 956-0266\smallbreak\ \ 
\ \ \href{mailto:jeremyggiese@gmail.com}{jeremyggiese@gmail.com}\\
\end{center}

\hrule
\vspace{-0.4em}
\subsection*{\Large{Experience:}}

%\begin{itemize}
	\parskip=0.1em

	%\item
	\headerrow
		{\textbf{Marshall University}}
		{\textbf{Huntington, WV}}
	\\
	\headerrow
		{\hspace{0.5cm}\emph{Intern with Department of Education of West Virginia}}
		{\emph{July 2019 --January 2020}}
	\begin{itemize*}
		\item Validated the functionality of applications before they were released to users.
		\item Determined a standard for internal testing and performed testing against one Domain.
		\item Using the determined standard developed an Automated Penetration Testing program which runs against any domain and determines the security of the domain.
		\end{itemize*}

	%\item
	\headerrow
		{\hspace{-0.5cm}\textbf{Dollar General}}
		{\textbf{Lewisburg, WV}}
	\\
	\headerrow
		{\hspace{0.5cm}\emph{Sales Associate}}
		{\emph{July 2018 -- August 2018}}
	\begin{itemize*}
		\item Assisted Customers in finding items.
		\item Ensured the store was clean and appealing to customers.
		\item Checked out customers giving the correct change for their purchase.
	\end{itemize*}

	%\item
	\headerrow
		{\hspace{-0.5cm}\textbf{McDonald's}}
		{\textbf{White Sulphur Springs, WV}}
	\\
	\headerrow
		{\hspace{0.5cm}\emph{Team Member}}
		{\emph{June 2016 -- July 2018}}
	\begin{itemize*}
		\item Entered orders given by customers
		\item Gave customers orders
		\item Checked on customers after a period of time to ensure they were enjoying their meal.
	\end{itemize*}

%\end{itemize}


\hrule
\vspace{-0.4em}
\subsection*{\Large{Education:}}

%\begin{itemize}
	\parskip=0.1em

	%\item 
	\headerrow
		{\textbf{B.S. Computer Science, Marshall University}}
		{\textbf{Huntington, WV}}
	\\
	\headerrow
		{\emph{College of Information Technology \& Engineering}}
		{\emph{August 2016- May 2020}}
	\begin{itemize*}
		\item Major: Computer Science
		\item Minor: Mathematics
		%\item Overall GPA: 3.11
		%\item Major GPA: 3.56
	\end{itemize*}
	\begin{description*}
	\item[\textbf{Capstone Project:}] 
	Using a team structure, determined requirements as given by client. After gathering requirements team setup development schedule. Finally the team developed and implemented a Unity AR application which visualizes data structures to aid in-course explanation.
	
	\end{description*}
%\end{itemize}


\hrule
\vspace{-0.4em}
\subsection*{\Large{Core Technical Skills:}}

\begin{indentsection}{\parindent}
\hyphenpenalty=1000
\begin{description*}
	\item[Technologies:]
	C, \CPP, Java, \LaTeX, Python, Shell Script, SQL, Laravel, Selenium, Docker
	%\item[Open Source Contributions:]
	%Project A, Project B, Project C
\end{description*}
\end{indentsection}

\hrule
\vspace{-0.4em}
\subsection*{\Large{Personal Work:}}

\begin{indentsection}{\parindent}
\hyphenpenalty=1000
\begin{description*}
	\item[\href{https://github.com/jeremyggiese/jgieseRepo/tree/master/Economics}{Basic Economics Application}]
	Solves Economics problems, developed for a difficult course. GUI will solve based on inputs given, if possible. The GUI is very slow and can take many seconds to find the answer.
	\item[\href{https://github.com/jeremyggiese/jgieseRepo/tree/master/iOS/Finances}{Basic Finances Application}]
	Tracks finances and helped me to understand OOP in Swift. Uses basic Object Oriented Programming to save a finances Object to device storage, can be repeated many times.
	\item[Portable 12V Display]
	Allowed the use of an old laptop display as an external monitor. Built from an Acer Laptop screen and a driver board.
		
	%\item[Open Source Contributions:]
	%Project A, Project B, Project C
\end{description*}
\end{indentsection}

%\hrule
%\vspace{-0.4em}
%\subsection*{References:}
%
%\begin{indentsection}{\parindent}
%\hyphenpenalty=1000
%\begin{description*}
%	\item[Paulus Wahjudi:]
%	\href{mailto:wahjudi@live.marshall.edu}{wahjudi@live.marshall.edu}
%	\item[James Fuller:]
%	\href{mailto:fullerj@live.marshall.edu}{fullerj@live.marshall.edu}
%	%\item[Open Source Contributions:]
%	%Project A, Project B, Project C
%\end{description*}
%\end{indentsection}


\end{document}
